\documentclass[a4paper,12pt]{article}
\usepackage{TLCresume}
\begin{document}

% ====================
% EXPERIENCE A
% ====================

\subsection*{\large AI.lab UnB \hfill January 2024 --- july 2025}
\subtext{\hfill Brasília, DF}
\vspace{0.5em}

Work on the high-impact Osiris Project, resulting from an \textbf{investment of \$700,000 USD}, developing AI applications to streamline workflows for \textbf{judges and prosecutors} in tax enforcement. Held dual roles as Data Scientist and Backend Developer.

\subsubsection*{\small \textit{Backend Developer}}
\vspace{-1.3em}
\subtext{\tiny  August 2024 --- july 2025}
\vspace{-0.5em}
\begin{zitemize}
    \item Develop APIs and AI services to integrate machine learning models aimed at improving the work of judges and prosecutors in tax enforcement.
    \item Deploy models to production using \textbf{FastAPI}, \textbf{Docker} containers, and \textbf{MLOps} practices.
    \item Implement unit and integration tests using \textbf{Pytest}.
    \item Apply \textbf{parallel and distributed} programming techniques to achieve a \textbf{5x reduction in processing time}.
    \item Create new modules following a \textbf{microservices} architecture.
\end{zitemize}

\subsubsection*{\normalsize \textit{Data Scientist}}
\vspace{-1.3em}
\subtext{\tiny January 2024 --- August 2024}
\vspace{-0.5em}
\begin{zitemize}

  \item Used \textbf{MLflow} for versioning and developing \textbf{pipelines for AI} models.  
  \item Utilized \textbf{MLflow} for model \textbf{performance analysis} and testing different hypotheses.  
  \item Implemented efficient pipelines for preprocessing (data mining, cleaning, and augmentation), vectorization, and storage of textual data.  
  \item Leveraged LLMs such as \textbf{Llama 3}, along with \textbf{RAG} techniques and \textbf{NLP} for legal text classification.  
  \item Developed and deployed highly accurate \textbf{(90\%)} classification models for legal documents,
  \item Applied \textbf{Machine Learning} (scikit-learn) and \textbf{Deep Learning} (PyTorch, TensorFlow).  
\end{zitemize}

% ====================
% EXPERIENCE B
% ====================
% \vspace{1.5em}
% \vspace*{7pt}
% \vspace{1.5em}
%
% \subsection*{\large Zeroo \hfill September 2022 --- November 2023}
% \subtext{Android Developer \hfill Brasília, DF}
%
% \vspace{-0.5em}
% \begin{zitemize}
%     \item Developed native Android app using Java/Kotlin
%     \item Integrated \textbf{AI models} for object classification with \textbf{TensorFlow} and \textbf{ML Kit}
%     \item Created requirements documentation using Mkdocs
%     \item Implemented MVVM architecture with SOLID principles and \textbf{GOF patterns}
%     \item Built relational database using \textbf{SQLite3} with Room and LiveData
% \end{zitemize}

% ====================
% EXPERIENCE C
% ====================
\vspace{1.5em}
\vspace*{7pt}
\vspace{1.5em}

\subsection*{\large University of Brasília  \hfill March 2022 --- August 2022}
\subtext{Data structures \& Algorithms teaching assistant \hfill Brasília, DF}
\vspace*{3pt}

Enhanced expertise in algorithms while developing technical communication skills:

\begin{zitemize}
    \item Greedy algorithms
    \item Dynamic Programming
    \item Tree structures
    \item Graph theory
    \item Complexity analysis (Big-O)
\end{zitemize}

\end{document}
